\documentclass[letterpaper,11pt]{article}
\usepackage[top=0.75in, bottom=0.25in, left=0.75in, right=0.75in]{geometry}

\usepackage{latexsym}

\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[sfdefault]{noto}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-9pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[3]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} \textbar \textit{ #2} & #3 \\
    \end{tabular*}\vspace{-7.5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\textbf{\Large NORMAN BUI}} \\ \vspace{1pt}
    \small +1 613-983-3217 $|$
    \href{mailto:normanbui@cmail.carleton.ca}{\underline{normanbui@cmail.carleton.ca}} $|$
    \href{https://www.linkedin.com/in/normanbui23/}{\underline{linkedin.com/in/normanbui23}} $|$
    \href{https://github.com/nbui23}{\underline{github.com/nbui23}}
    % \href{https://devpost.com/normanbui23}{\underline{devpost.com/normanbui23}}
\end{center}

%-----------EDUCATION-----------
\section{\textbf{\Large Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Carleton University}{Bachelor of Computer Science (Honours), \textbf{3.9/4.0 GPA}}{{Expected April 2026}}
      \resumeItemListStart
        % \resumeItem{Minor in Psychology}
        \resumeItem{Awards: Deans' Honours List, President's Scholars Scholarship, Chalmers Jack Mackenzie Scholarship}
        \resumeItem{Relevant Coursework: Data Structures \& Algorithms, Discrete Math, Web Apps, Operating Systems, Object-Oriented Software Engineering, Statistics, Programming Paradigms, Human-Computer Interaction (UI/UX), Databases}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{\textbf{\Large Experience}}
  \resumeSubHeadingListStart

      \resumeSubheading
      {Public Health Agency of Canada}{Junior Data Scientist - Python, ML, MDM, ETL }{Sep 2024 - Present}
      \resumeItemListStart
      \resumeItem{Contributing to a WHO-PHAC Master Data Management system using ML for entity matching across epidemiological datasets, improving data quality and parameter extraction accuracy for global health research.}
      \resumeItemListEnd

      \resumeSubheading
      {Bedarra Corporation}{Student Researcher - Python, LLM, RAG}{Aug 2024 - Present}
      \resumeItemListStart
      \resumeItem{Researching LLM and RAG systems to develop accurate AI assistants for researcher productivity-oriented projects.}
    %   \resumeItem{Developed a RAG system for Factor programming language queries, qualitatively increasing query response accuracy, through implementation of FLAN-T5 language model and FAISS vector store.}
    %   \resumeItem{Engineered a comprehensive knowledge base for Factor programming, covering 95\% of language features and best practices, by creating and structuring a detailed JSON corpus.}
    %   \resumeItem{Improved query processing speed by 30\% by integrating Sentence Transformers for efficient text embeddings and FAISS for similarity search.}
    %   \resumeItem{Enhanced system flexibility and maintainability through modular design and implementation of LangChain framework for RAG pipeline.}
    %   \resumeItem{Implemented an extensible corpus feature by designing a scalable JSON structure and data loading mechanism.}
      \resumeItemListEnd

      \resumeSubheading
      {Kongsberg Geospatial}{Software Engineer Intern - C++, Qt, Python, GIS}{May 2024 - Aug 2024}
      \resumeItemListStart
      \resumeItem{Built GIS-focused demos with C++, Qt, Git, and TerraLens SDK for ATC and defense applications.}
      \resumeItem{Implemented advanced map rendering (LiDAR, WMTS, S-57), object tracking, performance visualization (CPU, GPU, RAM), and UI enhancements for TerraLens demo, significantly boosting client satisfaction.}
        % \resumeItem{Developing C++ engineering solutions for TerraLens and IRIS in Qt, focusing on geographic information systems.}
        % \resumeItem{Calculated and visualized performance metrics and implemented map rendering for LiDAR, WMTS, and S-57.}
        \resumeItem{Developed a proof of concept script to handle ATC software's log processing with Python, \textbf{reducing processing time from days to seconds}.}
        \resumeItem{Aggregated various VFR and terrain data sources using Python scripting, \textbf{reducing processing time by 40\%}.}
        % \resumeItem{Added clicking functionality to moving objects using MouseEvents and coordinates to TerraLens demo, improving user interaction and experience.}
      \resumeItemListEnd

    \resumeSubheading
      {Health Canada}{Data Scientist Intern - Python, ML, NLP, ETL, Web Scraping}{Sep 2023 - Dec 2023}
      \resumeItemListStart
        \resumeItem{Developed Python solutions for chemical assessment, leading to improved risk data aggregation and analysis.}
        \resumeItem{Built random forest classifiers with pandas, NumPy, SciPy, and scikit-learn to accurately predict chemical toxicity.}
        \resumeItem{Restored web scraping scripts for chemical data aggregation using BeautifulSoup4 and lxml, \textbf{increasing risk data search functionality by 53.33\%}.}
        \resumeItem{Refactored federated search system and added session management, automatic retries, and dynamic rate limiting, significantly enhancing system maintainability and reliability.}
        \resumeItem{Developed automated workflow for extracting semantic triples from scientific articles using CoreNLP and Stanza, \textbf{streamlining the collection and organization of qualitative data} into a Neo4J knowledge graph.}
      \resumeItemListEnd

    \resumeSubheading
    {Department of National Defence}{Junior Software Developer - Python, LLM, RAG}{Jun 2023 - Nov 2023}
      \resumeItemListStart
        \resumeItem{Built a LLM RAG proof of concept with Flask and GPT-3.5 to simulate conversation with a local document database.}
        \resumeItem{Implemented a NLP pipeline with tokenization, context analysis, and named entity recognition using NLTK.}
        \resumeItem{Used SQLite3 and FAISS for efficient storage and embedding retrieval, enabling fast response times.}
      \resumeItemListEnd

    \resumeSubheading
    {NAV Canada}{Software Engineer Intern - C++, Qt, PowerShell, GIS}{May 2023 - Aug 2023}
      \resumeItemListStart
        \resumeItem{Developed C++ solutions for various ATC applications, resulting in improved performance and reliability.}
        \resumeItem{Implemented optimized data management strategies using C++ and Qt to achieve a \textbf{60\% reduction in directory clutter} and \textbf{improve automated analysis solutions by 30\%} in internal data extraction tool.}
        \resumeItem{Optimized code and resolved various bugs in ATC software, \textbf{improving overall graphical performance by 6\%}.}
        \resumeItem{Automated network configurations using PowerShell, \textbf{reducing setup time from 30 minutes to seconds}.}
      \resumeItemListEnd

    \resumeSubheading
    {Correctional Service Canada}{Junior Wev Developer - C\#, .NET, Web App, QA}{May 2022 - Apr 2023}
      \resumeItemListStart
        \resumeItem{Improved victim services web application through accessbility testing and bug fixes, increasing user satisfaction.}
        \resumeItem{Improved front-end through accessibility testing and fixing bugs for \textbf{over 100 users daily}.}
        % \resumeItem{Resolved document generation errors in Dynamics 365, \textbf{reducing software downtime}}
      \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{\textbf{\Large Projects}}
    \resumeSubHeadingListStart

        \resumeSubheading{SocialSaplings}{HTML/SCSS, JavaScript, Bootstrap, Node, Express, Firebase (Firestore, Auth)}{\href{https://devpost.com/software/socialsaplings}{\underline{Devpost}}}
            \resumeItemListStart
                \resumeItem{Led the development of a reforestation web platform, securing \textbf{1st place overall} at KuriusHacks: March Edition.}
                % \resumeItem{Implemented a tool using GBIF, SoilGrids, Open-Elevation, and OpenWeatherMap to recommend optimal tree species based on a user's geodata.}
                \resumeItem{Implemented a tool using various APIs to recommend optimal tree species based on a user's geodata.}
                \resumeItem{Developed a tree planting visualization tool with Google Maps API to showcase global reforestation impact.}
                \resumeItem{Added profiles, posts, likes, and comments, using Firebase for data management and authentication.}
            \resumeItemListEnd

        % \resumeSubheading{Pomodojo}{HTML/CSS, JavaScript, Bootstrap, Node, Express, MongoDB, WebRTC}{\href{https://devpost.com/software/pomodorm}{\underline{Devpost}}}
        %     \resumeItemListStart
        %         \resumeItem{Developed a study platform to facilitate productive Pomodoro sessions with gamification elements for motivation.}
        %         \resumeItem{Enabled real-time group video calling with \textbf{WebRTC and Agora APIs}, ensuring seamless, low-latency interaction.}
        %         \resumeItem{Used \textbf{MongoDB, Node, and Express} for a scalable backend, managing data persistence and session logistics.}
        %     \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{\textbf{\Large Skills}}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
    \item{
    \textbf{Languages}{: HTML/CSS, C/C++, C\#, Python, Java, SQL, JavaScript, PHP} \\
    \textbf{Frameworks \& Databases}{: Flask, Express, Bootstrap, WET, MySQL, SQLite3, PostgreSQL, Firebase, MongoDB, Neo4J, .NET} \\
    \textbf{Libraries}{: pandas, NumPy, matplotlib, scikit-learn, unittests, spaCy, OpenAI, Sentence Transformers, BS4, lxml, Selenium} \\
    \textbf{Development Tools}{: Git, Node, Ubuntu, Qt Creator, Postman, Balsamiq, Agile Methodology, SDLC, OOP} \\
    }}
  \end{itemize}
%-------------------------------------------
\end{document}
